### 2019-06-06 Manuscript/Manuscript.tex
Updates from Overleaf

The original surface extent LIP polygons were assigned a plate ID corresponding to a tectonic unit on Earth using the polygons of \citet{Torsvik2016a} for the Phanerozoic. The LIP polygons and tectonic units were reconstructed from 520~Ma to the present (e.g. Fig. \ref{fig:Reconstruction_Snapshots}) utilizing the paleogeographic model of \citet{Torsvik2016a} in the spin axis reference frame (anchor plate ID of 1). This paleogeographic model was updated to include revisions to Ordovician Laurentia \citep{Swanson-Hysell2017a} and Paleozoic Asia \citep{Domeier2018a}. Reconstructions and area calculations within latitude bands utilized the pyGPlates function library and custom Python scripts. The total LIP area and the LIP area reconstructed within the tropical rain belt were calculated for the various decay and burial scenarios at a resolution of 5~Myr (Fig. \ref{fig:LIP_Areas}B and C). All the data and code necessary to reproduce the analyses and figures presented in this study can be downloaded from GitHub (\url{https://github.com/Swanson-Hysell-Group/Large_Igneous_Provinces}).

>>>>

The original surface extent LIP polygons were assigned a plate ID corresponding to a tectonic unit on Earth using the polygons of \citet{Torsvik2016a} for the Phanerozoic. The LIP polygons and tectonic units were reconstructed from 520~Ma to the present (e.g. Fig. \ref{fig:Reconstruction_Snapshots}) utilizing the paleogeographic model of \citet{Torsvik2016a} in the spin axis reference frame (anchor plate ID of 1). This paleogeographic model was updated to include revisions to Ordovician Laurentia \citep{Swanson-Hysell2017a} and Paleozoic Asia \citep{Domeier2018a}. Reconstructions and area calculations within latitude bands utilized the pyGPlates function library and custom Python scripts. The total LIP area and the LIP area reconstructed within the tropical rain belt were calculated for the various decay and burial scenarios at a resolution of 5~Myr (Fig. \ref{fig:LIP_Areas}B and C). All the data and code necessary to reproduce the analyses and figures presented in this study can be downloaded from GitHub (\url{https://github.com/Swanson-Hysell-Group/2019_large_igneous_provinces}).
